### 2018-05-07 dissertation.tex
beta version :)

% SUMMARY HERE (300 word limit for most subjects):
This thesis addresses three questions on political and criminal violence. The first essay is an empirical evaluation of a broad set of homicide reduction policies implemented in the state of São Paulo, Brazil. I employ the synthetic control method, a generalisation of differences-in-differences, to compare these measures against an artificial São Paulo. The results indicate a large drop in homicide rates in actual São Paulo when contrasted with the synthetic counterfactual, with about 20,000 lives saved during the period.

@@

In the third essay, I employ extreme bounds analysis and distributed random forests to identify the key determinants of state-sponsored violence. Although the literature on mass killings has grown significantly over the last decades, it remains unclear whether estimates are robust to different model specifications or which variables accurately predict the onset of genocides and politicides. To address this issue, I test the sensitivity of 40 variables on a sample of 177 countries from 1945 to 2013. The results show that GDP per capita, the post-Cold War period, and stable political regimes are negatively associated with mass killings. In contrast, ethnic diversity, civil wars, and previous political turmoils increase the risk of state-led violence. Mass killings that occur during civil wars are correlated with a different set of variables, and I find that territorial conflicts and the use of militias are negatively associated with the outcome. The random forests estimations indicate that years since the last episode of mass violence, GDP per capita, urban population, ethnic polarisation, the number of military personnel, and democracy make the greatest contribution to the models' out-of-sample predictive power.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% ACKNOWLEDGEMENTS HERE:
I would like to extend thanks to the many people, in many countries, who so generously contributed to the work presented in this thesis. First and foremost, I want to thank my supervisor, Professor David Skarbek, for the guidance and encouragement he provided me. David was not only an excellent supervisor but also a great friend; his empathy, enthusiasm, and sense of humour made my stay at King's College a very pleasant one. I could not have wished for a better mentor for my PhD studies. Thank you very much.

@@

Completing this work would have been all the more difficult were it not for the support and constructive criticism provided by my friends. Specially, I would like to thank Veronica Adaeva, André Amaro, Paulo Roberto Araujo, Aline Bagatin, Fábio Barros, Michel Hulmann, Guilherme Kerr, Maurício Pantaleão, Letícia Sene, and the participants of academic seminars at King's College London, the Mercatus Center at George Mason University, and the Prometheus Institute in Berlin. I am deeply indebted to them for their insightful comments and hard questions.

I am also deeply thankful to several present and past members of the Friedrich Naumann Foundation for Freedom. Some years ago, I had received a scholarship to attend a short course in Germany, and that first experience abroad has transformed my life ever since. The present work is, to a large extent, a result of the push I received from the Naumann Foundation almost 10 years ago. I owe a great debt of gratitude to Cidália Achten, Gulmina Bilal, Rainer Erkers, Beate Forbriger, Verena Gierszewski, Birgit Lamm, Monica Lehmann, Stefan Melnik, and Wulf Pabst for their support. As time goes on, it is easy to see the huge impact they have had on my academic career.

>>>>

% SUMMARY HERE (300 word limit for most subjects):
This thesis addresses three topics in political and criminal violence. The first essay is an empirical evaluation of a broad set of homicide reduction policies implemented in the state of São Paulo, Brazil. I employ the synthetic control method, a generalisation of differences-in-differences, to compare these measures against an artificial São Paulo. The results indicate a large drop in homicide rates in actual São Paulo when contrasted with the synthetic counterfactual, with about 20,000 lives saved during the period.

@@

In the third essay, I employ extreme bounds analysis and distributed random forests to identify the key determinants of state-sponsored violence. Although the literature on mass killings has grown significantly over the last decades, it remains unclear whether estimates are robust to different model specifications or which variables accurately predict the onset of genocides and politicides. To address these issues, I test the sensitivity of 40 variables on a sample of 177 countries from 1945 to 2013. The results show that GDP per capita, the post-Cold War period, and stable political regimes are negatively associated with mass killings. In contrast, ethnic diversity, civil wars, and previous political turmoils increase the risk of state-led violence. Mass killings that occur during civil wars are correlated with a different set of covariates, and I find that territorial conflicts and the use of militias are negatively associated with the outcome variable. The random forests estimations indicate that years since the last episode of mass violence, GDP per capita, urban population, ethnic polarisation, the number of military personnel, and democracy make the greatest contribution to the models' out-of-sample predictive power.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% ACKNOWLEDGEMENTS HERE:
I would like to extend thanks to the many people, in many countries, who so generously contributed to the work presented in this thesis. First and foremost, I want to thank my supervisor, Professor David Skarbek, for the guidance and encouragement he provided me throughout this research. David has been very supportive since the first time we met, and his dynamism, vision, empathy, and great sense of humour have deeply inspired me. I could not have wished for a better supervisor for my PhD studies. Thank you very much.

@@

Completing this work would have been all the more difficult were it not for the support and constructive criticism provided by my friends. Specially, I would like to thank Veronica Adaeva, André Amaro, Paulo Roberto Araujo, Aline Bagatin, Fábio Barros, Michel Hulmann, Guilherme Kerr, Maurício Pantaleão, Letícia Sene, and the participants of academic seminars at King's College London and the Prometheus Institute in Berlin. I am deeply indebted to them for their insightful comments and hard questions.

I am also sincerely thankful to several present and past members of the Friedrich Naumann Foundation for Freedom. In 2009, I received a scholarship to attend a short course in Germany, and that first experience abroad has transformed my life ever since. The present work is, to a large extent, a result of the push I received from the Naumann Foundation almost 10 years ago. I owe a great debt of gratitude to Cidália Achten, Gulmina Bilal, Rainer Erkers, Beate Forbriger, Verena Gierszewski, Birgit Lamm, Monica Lehmann, Stefan Melnik, and Wulf Pabst for their support. As time goes on, it is easy to see the huge impact they have had on my academic career.
